
\newpage{}

\begin{abstract}
 \noindent 
Education system forms the backbone of every nation. And hence it is important to provide a
strong educational foundation to the young generation to ensure the development of open-minded
global citizens securing the future for everyone. Advanced technology available today can play a
crucial role in streamlining education-related processes to promote solidarity among students,
teachers, parents and the school staff.\\\\
Education is central to development. It is one of the most powerful instruments for reducing
poverty and inequality and lays a foundation for sustained economic growth. With this aim
currently our government has given special emphasis to the educational sector and school
improvement activities such as continuous professional development for teachers, training and
upgrading teachers and capacitating schools with manpower and materials are among the major
actions which have been taken in both primary and secondary schools. \\\\
In order to facilitate and simplify these actions one of the major tool is to have automated school management system.
School Management System(SMS) consists of tasks such as registering students, attendance
record keeping to control absentees, producing report cards, producing official transcript,
preparing timetable and producing different reports for teachers, parents,and officials.\\\\
Automation is the utilization of technology to replace human with a machine that can perform
more quickly and more continuously. By automating SMS documents that took up many large
storage rooms can be stored on few disks. Transcript images can be annotated. It reduces the time
to retrieve old transcripts from hours to seconds. However, the school system in the government
schools of Pakistan is not automated and the record officers generate transcripts and reports
manually and the school administrators use their experienced knowledge of miss and hit
approaches to prepare timetables.
%\vspace{0.89mm}
%
%\begin{equation}
%stackrel[u]{v}{T}=\stackrel[u]{v}{L}+\stackrel[u]{v}{L}\underset{W\epsilon V\cap w\neq u}{\sum}\stackrel[v]{w}{L}
%\end{equation}

%\pagenumbering{roman}% added the roman page number in the starting pages
\thispagestyle{empty}% to remove the page number
\end{abstract}
