\chapter{Conclusion and Future Work}
\label{chp5}
\section{Conclusion}
In conclusion, a database is a far more efficient mechanism to store and organize data than
spreadsheets; it allows for a centralized facility that can easily be modified and quickly shared among
multiple users. Having a web based front end removes the requirement of users having to understand
and use a database directly, and allows users to connect from anywhere with an internet connection and a basic web browser. It also allows the possibility of queries to obtain information for various surveys.
Due to the number of users reading and modifying student data in the department, it is an ideal use for
such a system.
\section{Strengths of The Proposed System}
Some of the proposed system functions and features will be describe in this section:
\begin{enumerate}
\item The most important feature of the proposed system is security, which will provide more security to the system such as login with username and password, the system will not allow any user to access the system unless they have user ID and password.
\item The proposed system will provide function of registering student in to the system by the administrator.
\item The proposed system will provide function where by the administrator can add new secretary and new teacher in to the system.
\item The proposed system provides function where by the teacher can enter student marks in to the system and calculate student grade. However, the proposed system includes so many other features which are not presented in the current system.
\item The Proposed system comes with the function of generating students report card.
\item The proposed system comes with the function of creating time table as well as printing the time table
\end{enumerate}

\section{Future Work}
In this report, we have reported a novel idea to design School Management System. But as there is always room for improvement, this idea can be improve more following are the future work for this SMS.
\begin{enumerate}
\item We can create an app which will deal the management of the school institutions.
\item We can create that app to make it work for the off line use as well as.
\item We can create this in more efficient way to fully utilize other requirement of the school management. 
\end{enumerate}